---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# betterCallSal

<!-- badges: start -->
<!-- badges: end -->

The goal of betterCallSal is to make you aware of what Covid-19 is doing to the world

## Installation

You can install the released version of betterCallSal from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("betterCallSal")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zahrasalarian/betterCallSal")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(betterCallSal)
# Wrong format
period = c("5-6-2020","7-8-2020")
country = "US"
plot <- betterCallSal::drawCovidPlot(period,country)

####
# You Got error because your date format is not Correct
# Correct format
period = c("05-06-2020","07-08-2020")
country = "US"
plot <- betterCallSal::drawCovidPlot(period,country)
```

Lets see an example of global map

```{r worldMap, warning=FALSE, error=FALSE}
map <- betterCallSal::drawCovidMap("09-09-2020","Deaths")
map
```

You can also embed plots, for example:

```{r plot, echo = FALSE}
p <- betterCallSal::drawCovidPlot(c("04-05-2020","06-05-2020"),"US")
p
```
