---
title: "Gives all you want to know from Covid-19"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Gives all you want to know from Covid-19}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(betterCallSal)
```
## Want to get Covid-19's data from anyday you want easily?
## Use "updateCovid" function
### How to use it:
###### This function gets a date in string type as input and throws a dataframe containing columns such as number of deaths, confirmed cases and etc in that day.
###### The date format is like that: "mm-dd-yy"
###### Don't forget that you should't pass dates when Covid-19 hadn't appeared yet
###### an example:
```{r updateCovid, warning=FALSE}
data <- updateCovid("06-10-2020")
View(data)
```
## Want to see world map of Covid-19's number of Deaths or confirmed cases?
## Use "drawCovidMap" function
### How to use it:
###### This function gets date the type of information you want to know as input and throws a leaflet map of all countries and you can see how many deaths or confirmed cases where in each country or even state in that specific date
###### The date format is like that: "mm-dd-yy" and the format of type should be either "Deaths" or "Confirmed".
###### Again don't forget that you should't pass dates when Covid-19 hadn't appeared yet
###### Examples:
```{r drawCovidMap, warning=FALSE}
deaths_map <- drawCovidMap("06-10-2020","Deaths")
deaths_map
confirmed_map <- drawCovidMap("06-10-2020","Confirmed")
confirmed_map
```
## Want to draw the plot of the number of covid-19 deaths and confirmed cases during a time series in a specific country?
## Use "drawCovidPlot" function
### How to use it:
###### This function gets a vector containing the start and end date of the time series and the name of a specific country as input and throws a ggplot barplot which it's y-axis is the number of deaths and confirmed cases in that especific country.
###### The date format is like that: "mm-dd-yy" and the format of type should be either "Deaths" or "Confirmed".
###### Again don't forget that you should't pass dates when Covid-19 hadn't appeared yet
###### An example:
```{r drawCovidPlot, warning=FALSE}
deaths_plot_1 <- drawCovidPlot(c("05-13-2020","06-10-2020"),"US")
deaths_plot_1
confirmed_plot_2 <- drawCovidPlot(c("05-13-2020","10-01-2020"),"China")
confirmed_plot_2
```
